Type cones of $\b{g}$-vector fans

### 2018-10-12 thirdPaper/draft/typeConeAssociahedra.tex
Sections 2.2.1 and 2.2.2

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}

@@

% polytopes
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector

@@

% Graph associahedra
\newcommand{\ground}{\mathrm{V}} % ground set
\newcommandx{\graphG}[1][1=G]{\mathrm{#1}} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}{\mathcal{T}} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nestedFan}{\mathcal{F}} % nested fan
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices

% SPECIFIC NON-KISSING COMPLEX

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom

% walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible

% GEOMETRY
% d-vectors
\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
\newcommand{\hs}{\mathbf{H}^{\le}} % half space
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}
\newcommand{\koszul}{^!} % duality

@@

\begin{notation}
For any two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
These coefficients are \apriori{} defined up to rescaling, but we additionally fix the rescaling so that~${\coefficient[\ray][\rays][\rays'] + \coefficient[\ray'][\rays][\rays'] = 1}$.
\end{notation}

@@

@@

Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
\begin{itemize}
\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
\end{itemize}

We say that the fan~$\Fan$ is \defn{coherent} if for any two exchangeable rays~$\ray, \ray'$ of~$\Fan$, the linear dependence
\vincent{Not sure of the choice of the name.}
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
does not depend on the pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$. These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.

@@

\begin{proof}
For~$\b{x}$ in~$P_\b{h}$, we have $\Psi(\b{x}) \ge 0$ by definition and~$\b{K}\Psi(\b{x}) = \b{K}\b{h} - \b{K}\b{G}\b{x} = \b{K}\b{h}$ since~$\b{K}$ is the left kernel of~$\b{G}$. Therefore~$\Psi(\b{x}) \in Q_\b{h}$.
Moreover, the map~$\Psi : P_\b{h} \to Q_\b{h}$ is:
\begin{itemize}
\item injective: Indeed, $\Psi(\b{x}) = \Psi(\b{x}')$ implies~$\b{G}(\b{x} - \b{x}') = 0$ and~$\b{G}$ has full rank since~$\Fan$ is essential and complete.
\item surjective: Indeed, for~$\b{z} \in Q_\b{h}$, we have~$\b{K}(\b{h}-\b{z}) = 0$ so that~$\b{h}-\b{z}$ belongs to the right kernel of~$\b{K}$ which is the image of~$\b{G}$. Therefore, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$. Therefore, $\b{z} = \Psi(\b{x}$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
\end{itemize}
\end{proof}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\blue}{\color{blue}} % blue command
\newcommand{\orange}{\color{orange}} % orange command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\uline{\textit{#1.}}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}

@@

% geometry
\newcommandx{\Asso}[2][1=n,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=n,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector
\newcommandx{\ray}[1][1=r]{\b{#1}} % ray
\newcommandx{\rays}[1][1=R]{\b{#1}} % rays
\newcommand{\gvector}[1]{\b{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\b{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}(#1)} % g-vector fan

@@

% Gentle associahedra
\newcommand{\quiver}{\bar Q} % quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommandx{\strings}[1][1=\quiver]{\mathcal{S}(#1)} % strings
\newcommandx{\distinguishableStrings}[1][1=\quiver]{\mathcal{S}_\mathrm{dist}(#1)} % distinguishable strings
\newcommandx{\walks}[1][1=\quiver]{\mathcal{W}(#1)} % walks
\newcommandx{\properWalks}[1][1=\quiver]{\mathcal{W}_\mathrm{prop}(#1)} % proper walks
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommandx{\NKC}[1][1=\quiver]{\mathcal{NK}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{RNK}(#1)} % reduced non-kissing complex
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommand{\hL}{\text{\rotatebox[origin=c]{180}{\checked}}}
\newcommand{\hR}{\text{\rotatebox[origin=c]{180}{\reflectbox{\checked}}}}
\newcommand{\cL}{\text{\reflectbox{\checked}}}
\newcommand{\cR}{\text{\checked}}
\newcommand{\hh}[1]{\hL#1\hR} % hook - hook
\newcommand{\cc}[1]{\cL#1\cR} % cohook - cohook
\newcommand{\hc}[1]{\hL#1\cR} % hook - cohook
\newcommand{\ch}[1]{\cL#1\hR} % cohook - hook

% Graph associahedra
\newcommand{\ground}{V} % ground set
\newcommandx{\graphG}[1][1=G]{#1} % graph
\newcommandx{\tube}[1][1=t]{\mathsf{#1}} % tube
\newcommandx{\tubes}{\mathcal{T}} % all tubes
\newcommandx{\tubing}[1][1=T]{\mathsf{#1}} % tubing
\newcommand{\connectedComponents}{\kappa} % connected components
\newcommand{\nestedComplex}{\mathcal{N}} % nested complex
\newcommand{\nonDisconnecting}{\mathrm{nd}} % non-disconnecting vertices
\newcommand{\neighbors}{\mathrm{ne}} % neighbors

%% SPECIFIC NON-KISSING COMPLEX
%
%% COMBINATORICS
%% quiver
%
%% walks
%\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
%\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
%\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
%\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
%\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
%\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign
%
%% non-kissing complex, lattice, flip graph
%\newcommand{\kn}{\kappa} % kissing number
%\newcommand{\KN}{\textsc{kn}} % Kissing Number
%\newcommandx{\NKC}[1][1=\quiver]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
%\newcommandx{\RNKC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
%\newcommandx{\NKL}[1][1=\quiver]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
%\newcommandx{\NKG}[1][1=\quiver]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
%\newcommandx{\NFC}[1][1=\quiver]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
%\newcommand{\peak}{\mathrm{peak}} % bottom dissection
%\newcommand{\deep}{\mathrm{deep}} % top dissection
%\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
%\renewcommand{\top}{\mathrm{top}} % top
%\newcommand{\bottom}{\mathrm{bot}} % bottom
%\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)
%
%% accordion and slalom complexes
%\newcommand{\surface}{\mathcal{S}} % an orientable surface
%\newcommand{\dual}{^*} % duality
%\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
%\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
%\newcommand{\edges}{\mathcal{E}} % edges of a dissection
%\newcommand{\faces}{\mathcal{F}} % faces of a dissection
%\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
%\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
%\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
%\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
%\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
%\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
%\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
%\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
%\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
%\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
%\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
%\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
%\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface
%
%% lattices
%\newcommand{\meet}{\wedge} % meet
%\newcommand{\join}{\vee} % join
%\newcommand{\bigMeet}{\bigwedge} % meet
%\newcommand{\bigJoin}{\bigvee} % join
%\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
%\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
%\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
%\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
%\newcommand{\projDown}{\pi_\downarrow} % down projection map
%\newcommand{\projUp}{\pi^\uparrow} % up projection map
%\newcommand{\JI}{\mathsf{JI}} % join-irreducible
%\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
%\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
%\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
%\newcommand{\ji}{\mathsf{ji}} % join irreducible
%\newcommand{\mi}{\mathsf{mi}} % meet irreducible
%
%% GEOMETRY
%% d-vectors
%\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
%\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
%\newcommandx{\dvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
%% g-vectors
%\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
%\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
%\newcommandx{\gvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
%% c-vectors
%\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
%\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
%\newcommandx{\allcvectors}[1][1=\quiver]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
%\newcommandx{\cvectorFan}[1][1=\quiver]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
%% points, hyperplanes, half-spaces
%\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
%\newcommandx{\ray}[1][1=r]{\mathbf{#1}} % ray
%\newcommandx{\rays}[1][1=R]{\mathbf{#1}} % rays
%\newcommand{\hs}{\mathbf{H}^{\le}} % half space
%\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
%\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
%\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
%\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
%
%% ALGEBRA
%\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
%\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
%\newcommandx{\AR}[1][1=\quiver]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
%\newcommandx{\tTC}[1][1=\quiver]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
%\newcommand{\rep}{\operatorname{{\rm rep}}}
%\newcommand{\proj}{\operatorname{{\rm proj}}}
%\newcommand{\koszul}{^!} % duality

@@

\begin{notation}
For any two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with~$\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, we denote by~$\coefficient[{\ray[s]}][\rays][\rays']$ the coefficient of~$\ray[s]$ in the unique linear dependence between the rays of~$\rays \cup \rays'$, \ie such that
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
These coefficients are \apriori{} defined up to rescaling, but we additionally fix the rescaling so that~${\coefficient[\ray][\rays][\rays'] + \coefficient[\ray'][\rays][\rays'] = 2}$ (this convention is arbitrary, but will be convenient in \cref{sec:applications}).
\end{notation}

@@

\begin{remark}
\label{rem:dimTypeCone}
Since the type cone is an open~$N$ dimensional cone with a linearity subspace of dimension~$n$, it has at least~$N-n$ facets.
We say that the type cone is \defn{simplicial} when it has precisely $N-n$ facets.
\end{remark}

@@

Two rays~$\ray$ and~$\ray'$ of~$\Fan$ are called \defn{compatible} if there are both contained in a cone of~$\Fan$ and \defn{exchangeable} if there are two adjacent cones~$\R\rays$ and~$\R\rays'$ of~$\Fan$ with ${\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}}$.
If~$\rays(\Fan)$ denotes the set of rays of~$\Fan$, a \defn{compatibility degree} for~$\Fan$ is a function~$\compatibilityDegree{-}{-}: \rays(\Fan) \times \rays(\Fan) \to \R$ such that
\begin{itemize}
\item $\compatibilityDegree{\ray}{\ray'} = -1$ if~$\ray = \ray'$ and is non-negative otherwise,
\item $\compatibilityDegree{\ray}{\ray'} = 0$ if ~$\ray$ and~$\ray'$ are compatible,
\item $\compatibilityDegree{\ray}{\ray'} > 0$ if~$\ray \ne \ray'$ are incompatible,
\item $\compatibilityDegree{\ray}{\ray'} = 1 = \compatibilityDegree{\ray'}{\ray}$ if and only if~$\ray$ and~$\ray'$ are exchangeable.
\end{itemize}
\vincent{The definition of compatibility degree is not really useful here.}

\begin{definition}
\label{def:coherent}
We say that the fan~$\Fan$ is \defn{coherent} if for any two exchangeable rays~$\ray, \ray'$ of~$\Fan$, the linear dependence
\vincent{Not sure of the choice of the name.}
\[
\sum_{\ray[s] \in \rays \cup \rays'} \coefficient[{\ray[s]}][\rays][\rays'] \, \ray[s] = 0.
\]
does not depend on the pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$, but only on the pair of rays~$\ray, \ray'$.
This implies in particular that the rays~$\ray[s]$ for which~$\coefficient[{\ray[s]}][\rays][\rays'] \ne 0$ belong to~$\rays \cup \rays'$ for any pair~$\{\rays, \rays'\}$ of adjacent cones of~$\Fan$ with $\rays \ssm \{\ray\} = \rays' \ssm \{\ray'\}$. These rays are thus called \defn{forced rays} for the exchangeable pair~$\{\ray, \ray'\}$.
\end{definition}

@@

\begin{proof}
For~$\b{x}$ in~$P_\b{h}$, we have $\Psi(\b{x}) \ge 0$ by definition and~$\b{K}\Psi(\b{x}) = \b{K}\b{h} - \b{K}\b{G}\b{x} = \b{K}\b{h}$ since~$\b{K}$ is the left kernel of~$\b{G}$. Therefore~$\Psi(\b{x}) \in Q_\b{h}$.
Moreover, the map~$\Psi : P_\b{h} \to Q_\b{h}$ is:
\begin{itemize}
\item injective: Indeed, $\Psi(\b{x}) = \Psi(\b{x}')$ implies~$\b{G}(\b{x} - \b{x}') = 0$ and~$\b{G}$ has full rank since~$\Fan$ is essential and complete.
\item surjective: Indeed, for~$\b{z} \in Q_\b{h}$, we have~$\b{K}(\b{h}-\b{z}) = 0$ so that~$\b{h}-\b{z}$ belongs to the right kernel of~$\b{K}$ which is the image of~$\b{G}$. Therefore, there exists~$\b{x} \in \R^n$ such that~$\b{h}-\b{z} = \b{G}\b{x}$. Therefore, $\b{z} = \Psi(\b{x})$ and~$\b{x} \in P_\b{h}$ since~$\b{h} - \b{G}\b{x} = \b{z} \ge 0$.\qedhere
\end{itemize}
\end{proof}

\begin{corollary}
\label{coro:simplicialTypeCone}
Assume that the type cone~$\typeCone(\Fan)$ is simplicial and let~$\b{K}$ be the $(N-n) \times N$-matrix whose rows are the outer normal vectors of the facets of~$\typeCone(\Fan)$. Then the polytope
\[
R_\b{\ell} \eqdef \set{\b{z} \in \R^N}{K\b{z} = \b{\ell} \text{ and } \b{z} \ge 0}
\]
is a realization of the fan~$\Fan$ for any positive vector~$\b{\ell} \in \R_{>0}^{N-n}$.
Moreover, the polytopes~$R_\b{\ell}$ for~$\b{\ell} \in \R_{>0}^{N-n}$ describe all polytopal realizations of~$\Fan$.
\end{corollary}
